The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-03-20 analysis/paper/paper.qmd

emu_theses_words <- emu_theses |> 
  select(title, text_clean) |> 
  unnest_tokens(output = word, input = text_clean) |>   # remove punctuation, convert to lowercase, separate all words
  anti_join(tidytext::stop_words, by = "word")
```

>>>>

emu_theses_words <- emu_theses |> 
  select(title, text_clean) |> 
  unnest_tokens(output = word, input = text_clean) |>   # remove punctuation, convert to lowercase, separate all words
  anti_join(tidytext::stop_words, by = "word")
